---
title: "Weight of Fish"
author: "Jason Leon"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```


### Best Two regressor model
Best two regression models are height and width

```{r}
Perchmodel <-lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```

The adjusted r-squared is 0.94 and the residual standard error is 85.17, with a p-value 2.2

## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

L1, L3 are the two best regression model. Best regression model is everything

### Best Models

```{r}
Pikebest <-lm(Weight~.,data=Pike)
summary.lm(Pikebest)
```

The r-squared is 0.9794 and the residual error is 70.86. The p-value is 8.679. This is the best model.

### Best Two regressor model
```{r}
Piketwo <-lm(Weight~Length1+Length3, data=Pike)
summary.lm(Piketwo)
```

This model summarizes put best two regression models. The residual standard error is 92.56. The r-squared is .09649 and the p- value is 2.572e-11. The smallest p-value has the best result.

## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

Best regression model is all of them. The best regression models is L1, L3.

### Best Models

```{r}
Roachrock <-lm(Weight~.,data=Roach)
summary.lm(Roachrock)

```

The residual standard error is 37.58. The r-squared is 0.821 and the p-value is 1.028e-05. This model holds the smallest p-value out of all the model we did so far.

### Best Two regressor model

```{r}
Roachbest <-lm(Weight~Length1+Length3, data=Roach)
summary.lm(Roachbest)
```

The residual standard error is 36.83. The r-squared is 0.08281 and the p-value is ata 1.23e-07. This is the second to smallest p-value out od all the charts/ models.

## Final Summary Statements

overall today in class we had to find for each of the three species of fish listed below, we had to determine the best regression model and also the best 2 element regression model while Using the Best Subset Regression helper file. so what we find out is Roachrock model holds the smallest p-value out of all the model we did. Pikebest was the best model out of the three and Perch was just in between them.


